Testing Success of Bayes Function on Varying COSMIC Signatures

### 2021-06-29 Varying Signature Function Testing.Rmd
plotted average misclassification rate for Bayes function vs. cosine similarities of COSMIC signatures to FFPE, implemented a function to plot an ROC curve for the Bayes function applied to a simulated sample of mutations from FFPE and one specified COSMIC signature

---
title: "Untitled"
author: "Audrey Mitchell"
date: "6/28/2021"
output: html_document
---

@@

```{r}
ggplot(cos.sim.misclass.data, aes(x = cosine_similarity, y = average_misclassification))+
  geom_point()+
  geom_smooth()+
  labs(title = "Average misclassification rate vs. cosine similarity to FFPE", x = "Cosine similarity of COSMIC signature to FFPE signature", y = "Average misclassification rate (10 iterations)")
```

@@

```
#MMR (Signature 6, cos similarity to ffpe = )
```{r}
plot_bayes_roc(cosmic.6, "MMR", 180, 20, 200)
```

@@

```{r}
cosmic.17b <- as.matrix(cosmic.signatures[,"SBS17b"])
plot_bayes_roc(cosmic.17b, "SBS17b", 180, 20, 200)
```

@@

```{r}
cosmic.30 <- as.matrix(cosmic.signatures[,"SBS30"])
plot_bayes_roc(cosmic.30, "SBS30", 180, 20, 200)
```

>>>>

---
title: "Testing Success of Bayes Function on Varying COSMIC Signatures"
author: "Audrey Mitchell"
date: "6/28/2021"
output: html_document
---

@@

```{r}
ggplot(data = cos.sim.misclass.data, aes(y = average_misclassification, x = signature))+
  geom_boxplot()
```

```{r}
ggplot(cos.sim.misclass.data, aes(x = cosine_similarity, y = average_misclassification))+
  geom_point()+
  geom_smooth(method = "lm")+
  labs(title = "Average misclassification rate vs. cosine similarity to FFPE", x = "Cosine similarity of COSMIC signature to FFPE signature", y = "Average misclassification rate (10 iterations)")+
  scale_x_log10()
  #label outliars on plot
  #geom_label(aes(signature))
```

@@

```
#MMR (Signature 6, cos similarity to ffpe = )
```{r}
plot_bayes_roc(cosmic.6, "MMR", 100, 100, 200)
```

@@

```{r}
cosmic.17b <- as.matrix(cosmic.signatures[,"SBS17b"])
plot_bayes_roc(cosmic.17b, "SBS17b", 100, 100, 200)
```

@@

```{r}
cosmic.30 <- as.matrix(cosmic.signatures[,"SBS30"])
plot_bayes_roc(cosmic.30, "SBS30", 100, 100, 200)
```
